Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-12 document/ms.tex
summary of simulated results

We generate synthetic catalogs from two qualitatively different rate
functions.
Both distributions are generated by a separable model
\begin{eqnarray}
\rate_\ratepars (\ln\period,\,\ln\radius) &=&
    \rate_\ratepars^{(\period)}(\ln\period)\,
    \rate_\ratepars^{(\radius)}(\ln\radius)
\end{eqnarray}
but fit using the full general model.
The first model---\modela---has a smooth occurence surface where both
distributions are smooth broken power laws.
The second---\modelb---is designed to be exactly the distribution inferred by
\citet{petigura} in the range that they considered and then smoothly
extrapolated outside that range.

For each catalog, we directly apply the inverse-detection-efficiency
procedure as implemented by \citealt{petigura}\footnote{Our implementation
exactly reproduces their results when applied to the published catalog.} and
our probabilistic method.

\paragraph{Results}
See \fig{synthetic-radius}.
As expected, the forward model is a much lower variance estimator.

>>>>

We generate synthetic catalogs from two qualitatively different rate
functions.
Both distributions are generated by a separable model
\begin{eqnarray}
\rate_\ratepars (\ln\period,\,\ln\radius) &=&
    \rate_\ratepars^{(\period)}(\ln\period)\,
    \rate_\ratepars^{(\radius)}(\ln\radius)
\end{eqnarray}
but fit using the full general model.
The first model---\modela---has a smooth occurence surface where both
distributions are smooth broken power laws.
The second---\modelb---is designed to be exactly the distribution inferred by
\citet{petigura} in the range that they considered and then smoothly
extrapolated outside that range.
The catalogs generated from these two models are shown in \fig{smooth-results}
and \fig{simulation-results}, respectively and the data are available online
at \dfmtodo{ADD SOME URL}.

For each catalog, we directly apply the inverse-detection-efficiency
procedure as implemented by \citealt{petigura}\footnote{Our implementation
exactly reproduces their results when applied to the published catalog.} and
our probabilistic method, marginalizing over the hyperparameters of the
Gaussian process regularization.
\Fig{smooth-results} and \fig{simulation-results} show the results of this
analysis in both cases.
In particular, the side panels compare the marginalized occurence rate
functions in period and radius to the true functions that were used to
generate the catalogs.
\Fig{smooth-results} shows that even if the true occurence rate is a smooth
function, the rate inferred by the inverse-detection-efficiency method can
appear to have sharp features.
In this first example---where the true distribution is well described by our
Gaussian process model---the probabilistic inference of the occurence rate is
both more precise and accurate.

In the second example, the true rate function includes a sharp feature chosen
to reproduce the result published by \citet{petigura}.
In this case, \fig{simulation-results} shows that the probabilistic
constraints on the occurence rate are less precise \emph{but more accurate}
than results using the inverse-detection-efficiency method.
At this point, the distributions inferred by these two different techniques
don't seem drastically inconsistent but the difference are most obvious as the
survey completeness goes to zero: exactly the region of interest.
